\documentclass[a4paper, 10pt]{article}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage[none]{hyphenat}
\geometry{top=0.7in, bottom=0.7in, left=0.5in, right=0.5in}

\hypersetup{
    colorlinks=false,
    urlcolor=black,
    linkcolor=black
}

\setlength{\parindent}{0pt}
\setlist{nosep}
\setstretch{1.15}

\begin{document}
\pagenumbering{gobble}

\href{https://jancyrusm.github.io}{\textbf{\Large Jan Cyrus M. Villar}} \hfill \href{mailto:jancyrus.villar@gmail.com}{jancyrus.villar@gmail.com} \\
San Pedro, Laguna \hfill \href{https://github.com/jancyrusm}{github.com/jancyrusm} \\
+63 965 342 7601 \hfill \href{https://linkedin.com/in/jancyrusm}{linkedin.com/in/jancyrusm}

\vspace{-1em}

\section*{Education}
\vspace{-1.5em}
\noindent\rule{\textwidth}{0.4pt}
\noindent \textbf{Polytechnic University of the Philippines} \hfill \textit{Oct 2020 – Oct 2024} \\
\textit{Bachelor of Science in Computer Engineering} \hfill Sta. Mesa, Manila \\
Major in System and Software Development

\vspace{-1em}

\section*{Experience}
\vspace{-1.5em}
\noindent\rule{\textwidth}{0.4pt}
\noindent \textbf{Quality Assurance Analyst Intern} \hfill \textit{Sept 2023 – Feb 2024} \\
Department of Science and Technology Central Office \hfill Bicutan, Taguig
\begin{itemize}[leftmargin=0.5in]
  \item Identified and documented software bugs, resulting in improved software quality and bridged communication between QA and development teams.
  \item Developed and executed comprehensive test plans and test cases, ensuring thorough manual software testing and reducing the risk of bugs reaching production.
  \item Wrote basic test automation scripts using Selenium and Python, increasing
        testing efficiency and coverage.
\end{itemize}
\noindent \textbf{ICT Department Intern} \hfill \textit{Sept 2022 – Oct 2022} \\
Comglasco Aguila Glass \hfill San Martin de Porres, Parañaque
\begin{itemize}[leftmargin=0.5in]
  \item Installed and configured computer systems and network devices, enabling
        seamless company operations and connectivity.
  \item Provided troubleshooting and technical support, utilizing AnyDesk for remote
        assistance and minimizing downtime.
  \item Assisted in managing IT asset inventory, contributing to accurate
        record-keeping and efficient resource allocation.
\end{itemize}
\noindent \textbf{Admin Department Intern} \hfill \textit{Nov 2019 – Dec 2019} \\
Master Coating Industrial Technology, Inc. \hfill Biñan, Laguna
\begin{itemize}[leftmargin=0.5in]
  \item Maintained company database, ensuring data accuracy and integrity.
  \item Digitized documents through data entry, improving accessibility and
        streamlining information retrieval.
  \item Supported various departments with clerical tasks, enhancing efficiency and
        productivity.
\end{itemize}

\vspace{-1em}

\section*{Projects}
\vspace{-1.5em}
\noindent\rule{\textwidth}{0.4pt}
\noindent \href{https://github.com/jancyrusm/display-laudrofill}{\textbf{LaundroFill}} \hfill \textit{HTML, CSS, JS, Node.js, C++}
\begin{itemize}[leftmargin=0.5in]
  \item Led the embedded system development and microcontroller programming of an IoT-based liquid detergent dispensing machine based on Arduino and Raspberry Pi.
  \item Designed and implemented the dispensing algorithm using C++.
  \item Utilized Figma for UI/UX design, Git for version control, and Node.js for server-side development.
\end{itemize}
\noindent \href{https://github.com/jancyrusm/mobile-dev-final-las-filipinas-chronicles}{\textbf{Las Felipinas Chronicles}} \hfill \textit{C\#, Unity}
\begin{itemize}[leftmargin=0.5in]
  \item Led the development of Las Felipinas Chronicles, a historical detective game utilizing Unity for game engine, C\# for scripting, and Asset Store resources for efficient development.
  \item Created game specifications and operating instructions.
\end{itemize}
\noindent \href{https://github.com/jancyrusm/game-dev-final-chroma}{\textbf{Chroma}} \hfill \textit{C\#, Unity}
\begin{itemize}[leftmargin=0.5in]
  \item Designed and developed a 2D adventure-fighting platformer RPG using C\# and Unity.
  \item Implemented a complex state machine in Chroma to manage character interactions and game progression.
  \item Maintained and updated gameplay features.
\end{itemize}

\vspace{-1em}

\section*{Skills}
\vspace{-1.5em}
\noindent\rule{\textwidth}{0.4pt}
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{Programming:} & C\#, C++, Python, JavaScript                          \\
  \textbf{Web Development:} & HTML5, CSS3, ES6, Node.js, Bootstrap, Firebase   \\
  \textbf{Software \& Tools:}     & Git, GitHub, Figma, Selenium, Arduino, AnyDesk, Unity \\
\end{tabularx}

\vspace{-1em}

\section*{Awards and Scholarships}
\vspace{-1.5em}
\noindent\rule{\textwidth}{0.4pt}
\noindent \textbf{DOST-SEI S\&T Undergraduate Scholar} \hfill \textit{2020 - 2024} \\
RA 7687 Scholarship Recipient

\end{document}
